Extended Data

### 2022-03-09 doc/manuscript/Dow_Extended_Data.Rmd
a bit of cleanup

---
title: ""
author:
output: 
  pdf_document:
    fig_caption: yes
    #toc: true # table of content true
    #toc_depth: 2  
header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[figure]{labelformat=empty}
                  \captionsetup[table]{labelformat=empty}
---
```{r eval = TRUE, echo=FALSE, warning=FALSE, results='hide'}
path_to_results <- paste0(dirname(dirname(getwd())), "/results/") #I was trying to read directly from results folder, but couldn't get it working.

@@

sample_size_by_year= "XX"
#chronologies_table="S4" #!!! Hand-numbered in tree-ring figure captions

>>>>

---
title: ""
author:
output: 
  pdf_document:
    fig_caption: yes
    #toc: true # table of content true
    #toc_depth: 2  
header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[figure]{labelformat=empty}
                  \captionsetup[table]{labelformat=empty}
---
```{r eval = TRUE, echo=FALSE, warning=FALSE, results='hide'}
path_to_results <- paste0(dirname(dirname(getwd())), "/results/")

@@
